Footpath Planning for Example-driven Procedural Road Networks

### 2020-04-15 paper/paper.tex
Update todo
Update TODO
Add note about standard road widths from Trafikverket to report

The lineage aspect of the OSM data is available through the OSM History Viewer, an online debugging tool that lets anyone freely view the change history of individual fetures in a commit history-like fashion. There is an option for editors to include a personal note with their changesets to include additional details or motivate why a change was made, but there is no guaratee that the data includes any information on the aquisition method used (OSM 2020). The history aspect of the SLU dataset is not freely available online, but the acquistion method is included in the file metadata on a per-object basis. Lantmäteriet uses internal codes to specifify the acquistion method, and these codes can be referred to in the product description the accompanies the map files. As the scope of this project is limited to making a broad comparison of the positional accuracy of the two datasets, only the required positional accuracy as described by the SLU product description will be used.
TODO: Dig deeper in the SLU dataset, how can one find the method of aquisition for Stockholm buildings, and its precision?

@@

% TODO: Update project plan

% TODO: Scrape road data with same coords as the large data run
% TODO: Organize large building and road datasets
% TODO: Script that imports both building and road data
% TODO: Reconstruct geometrical hashmap to take both polygons and lines
% TODO: Implement new geometrical hashmap in new script
% TODO: Assign default path widths (min)
% TODO: Per road, go over narby features and infer max width, log collisions (max width - min width)

@@

@@

>>>>

The lineage aspect of the OSM data is available through the OSM History Viewer, an online debugging tool that lets anyone freely view the change history of individual fetures in a commit history-like fashion. There is an option for editors to include a personal note with their changesets to include additional details or motivate why a change was made, but there is no guaratee that the data includes any information on the aquisition method used (OSM 2020). The history aspect of the SLU dataset is not freely available online, but the acquistion method is included in the file metadata on a per-object basis. Lantmäteriet uses internal codes to specifify the acquistion method, and these codes can be referred to in the product description the accompanies the map files. As the scope of this project is limited to making a broad comparison of the positional accuracy of the two datasets, only the required positional accuracy as described by the SLU product description will be used.
%TODO: Dig deeper in the SLU dataset, how can one find the method of aquisition for Stockholm buildings, and its precision?

@@

% TODO: Assign default road widths
% TODO: Implement closest edge distance (project end points on the other edge, get closest perpendicular distance) 
% TODO: Per road, go over nearby features and infer max width, log collisions (max width - min width)

@@

\section{Collision checks}

The default minimum widths were obtained from (Lantmäteriet, 20). The standard minimum width for a two-lane road in Sweden is 6.5 meters.

@@

\bibitem{trafikverket-20}
https://trafikverket.ineko.se/Files/sv-SE/71830/Ineko.Product.RelatedFiles/2020\_029\_vagar\_och\_gators\_utformning\_krav.pdf \\
